Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 introduction.tex

This paper is a case study of how the ATLAS experiment has ``broken free'' of
the traditional computational approach of high-throughput computing on
distributed resources to embrace new platforms, in particular high-performance
computers. Specifically, we discuss the experience of integrating PanDA WMS with
a DOE leadership computing facility called Titan to reach sustained production
scales of approximately 51M core-hours a years. We also discusses the
investigation of a task execution runtime system on Titan, that is based on the
pilot-abstractions and which allows advanced execution modes of the ATLAS
workload as well as the enhanced support for heterogeneous workloads such as
molecular dynamics.

>>>>

This paper is a case study of how the ATLAS experiment has ``broken free'' of
the traditional computational approach of high-throughput computing on
distributed resources to embrace new platforms, in particular high-performance
computers. Specifically, we discuss the experience of integrating PanDA WMS with
a DOE leadership computing facility called Titan to reach sustained production
scales of approximately 51M core-hours a year. We also discusses the
investigation of a task execution runtime system on Titan, that is based on the
pilot-abstractions and which allows advanced execution modes of the ATLAS
workload as well as the enhanced support for heterogeneous workloads such as
molecular dynamics.
